RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

#### Batch corrected
```{r PCA.batch, fig.width=10, fig.height=5}
fit = dream(geneExpr, ~ Batch, info)

@@

```{r predict.celltype}

X = as.matrix(df_pca[,2:200])

@@

# isexpr = rowSums(edgeR::cpm(gtex_count[,idx])>1) >= 0.3*ncol(gtex_count[,idx])
isexpr = filterByExpr(geneCounts[,idx], model.matrix(~CellType, info[idx,]))

>>>>

#### Batch corrected
```{r PCA.batch, fig.width=10, fig.height=5}
fit = dream(geneExpr, ~ (1|Batch), info)

@@

```{r predict.celltype}
X = as.matrix(df_pca[,2:200])

@@

# isexpr = rowSums(edgeR::cpm(gtex_count[,idx])>1) >= 0.3*ncol(gtex_count[,idx])
isexpr = filterByExpr(gtex_count[,idx], model.matrix(~SMTSD, gtex_sample[idx,]))
